\Title

### 2023-07-06 cover_letter/2023-07-07_coverletter.tex
cover

Given the substantial modifications we did to the original manuscript to reduce and clarify the different sections we do not provide a tracked changes version of the revision (such a document can be provided if needed). We provide a point by point response to the reviewers with references to the manuscript.

@@

In the following we will give response to reviewers in \noteRev{framed boxes.}

@@

 \noteRev{Overall, we would like to thank Reviewer 1 for its comments that allowed us to focus on reshaping the manuscript and give clearer and shorter explanation of the work we submit in your journal. Because we did major modifications in the manuscript, we do not provide a tracked changes version of the revision but we can easily provide one if needed. }

\begin{quote}
 1. There is a lack of an intuitive figure to show the HD-SNN model used in this paper.
\end{quote}

 \noteRev{We provide such a figure in the new manuscript: Figure 3, P9}

\begin{quote}
 2. The MLR model used in the experimental part was presented in authors’ another work. Therefore, the changes on the MLR model are suggested to be highlighted and contrasted graphically.
\end{quote}

@@

\begin{quote}
 3. The title of section 2.2.1 is ’’a generative model for rater plots’’, but actually this section introduces basic terms and symbols. Section 2.2.2 is named ‘’detecting spiking motifs’’, but most of the content seems to introduce the generation process of raster plots, while only the last paragraph introduces the detection of motif. It is recommended that the content of these two sections be reorganized and that references to Figure 1(b)(c)(d) be added where appropriate during the description.
\end{quote}

@@

\begin{quote}
 4. The adjustment of weights and delays needs more detailed elaboration, preferably given in mathematical formulas.
\end{quote}

 \noteRev{We improved the mathematical formulation of the model in sections 2.2.1 and 2.2.2 and hope that it clarifies the general framework we use. Regarding training, it is described more clearly in P9, L313. Demonstration of the mechanism and the analogy with Hebbian learning was done in~\cite{grimaldi_robust_2022} and was not reproduced here. We hope this new version offers a clearer methodology.}

\begin{quote}
 5. In Figure 4, it is claimed that the kernels are very similar for the ON polarities, and different kernels are selective to the different motion directions. However, in terms of these two observations, I think they are not very significant, so I suggest a more intuitive way to reflect them, such as quantifying the similarity between the ON kernels, and the angle between the kernels and the vector of the standard motion directions. 
\end{quote}

 \noteRev{We gave a better explanation of the symmetry assumption in the methods (P9, L303) an how this new model uses this invariance in its computation like observed in complex cells. Indded, we don't want the polarity to have an impact on the classification and then this observation does not apply to the revised manuscript as it is a prior and not an emergent property.}

\begin{quote}
 6. There are few experiments and lack of comparative experiments. Since the model has an improvement based on MLR model, it is suggested to increase the comparison with MLR model and HOTS model on other datasets, such as N-MNIST and other neuromorphic datasets, so as to show the advantages of the proposed model in computational consumption.
\end{quote}

 \noteRev{The reviewer is making a good point but regarding the deadline for the revision and some objectives we focused on to improve the manuscript we could not apply the model on DVS recordings.}

\begin{quote}
 7. Some sections are verbose, such as the discussion.
\end{quote}

 \noteRev{We significantly changed the introduction (section 1), the methods (section 2) and the discussion (section 4) to address this comment. We hope to provide a more concise and clear explanation of our study.}

\begin{quote}
 8. There are some minor errors in the text, and it is recommended to check the full text: 
 1)In the first paragraph on page 8, "a presynaptic address $b_s$" should be "a postsynaptic address $b_s$"; 
 2)Whether $W_b$ in the first formula should be $K_b$? And d in it lacks description. 
 3)"PGs" should be given in its full name when it first appears. 
 4)There is no subgraph label of (a), (b) and (c) in Fig. 3, but the expression of Fig. 3-(a)/(b)/(c) appears many times. 
 5)The content of paragraph 1 on page 13 is repeated. 
\end{quote}

 \noteRev{We corrected these minor errors and thank the reviewer for reporting them.}

\textbf{Reviewer \#2}

\begin{quote}
 {\it Key results: Please summarize what you consider to be the outstanding features of the work.}
 Using a single layer of spiking neurons with heterogeneous delays to learn spatio-temporal  spiking motifs
\end{quote} 
\noteRev{We would like to thank reviewer \#2 for his comments. We have thoroughly revised the manuscript to take them into account.}

\begin{quote}
 The work presented here is very similar to the author's other work,  "Learning hetero-synaptic delays for motion detection in a single layer of spiking neurons" 10.1109/ICIP46576.2022.9897394. This must be addressed and cited with an explanation of how this work presented is an extension of this previous publication. Abstract, Fig 6 and the main result is presented in the previous work. Arguably some of the figures from the previous publication would be nice to see in this publication as it helps with the visualisation of the problem. One suggestion for the extension to make the work unique would be to extend with some event-camera data, as it is mentioned multiple times within the publication. 
 There are also a number of citations that could have been added that did appear in the other publication, while also including other motion detection/ segmentation or previous work on event-based optical flow, which is a very similar problem.
\end{quote}

\noteRev{In fact, there was no mention of this previous work in the original manuscript, as this 4-page paper had not yet been published in the proceedings of the conference at which it had been presented. As mentioned in the responses to reviewer \#1 in this cover letter, we have now added this citation~\cite{grimaldi_learning_2022}. In addition, in this submitted manuscript we describe the main differences from that previous study: the use of a more ecological task (Section 2.1), a complete formulation of the model (Section 2.2), and the improvements made in this particular model (P8, L285). We also provide citations to studies using similar methods (P8, L259). Further results are presented, especially the testing of the learned model with parametric textures.}

\bibliographystyle{plainnat}
\bibliography{FastMotionDetection}

>>>>

We thank the reviewer for the positive assesment which encouraged us to further improve our manuscript. Given the substantial modifications we did to the original manuscript to reduce and clarify the different sections we do not provide a tracked changes version of the revision (such a document can be provided if needed). We provide below a point by point response to the reviewers with references to the manuscript.

@@

In the following we will give response to reviewers using: \noteRev{framed boxes.}

@@

\begin{quote}
	The author's organization of the paper is much clearer than last time, and I suggest making the following modifications:
	1. For the natural-like texture images used, the author carried out some operations, such as changing texture parameters, etc. I suggest that the authors give 1-2 examples of these images corresponding to the different subgraphs in Figure 5, such as isotropic textures and grating-like textures.
\end{quote}

 \noteRev{We thank the reviewer for his constructive comment. This encouraged us to extend our task from using natural-like textures to actual natural images. This was further extended by using biologically inspired eye movements. We have kept the use of the synthetic textures in order to assess the relevant image parameters that are relevant for motion detection and we have drawn the analogies of our model with that found in the neurophysiological and psychophysical literature. We have added subgraph inset to illustrate the changes in parameters to the generation of figures.}

\begin{quote}
	2. Experiments that assess accuracy should be repeated many times (and give deviation) to eliminate data uncertainty.
\end{quote}

@@

\begin{quote}
	3. I would still recommend that the authors add experiments on other data sets, or compare with other works  on the current data set.
\end{quote}

@@

\begin{quote}
	4. There are two “observe” in line 355.
\end{quote}

 \noteRev{Fixed.}
